\Huge Handwritten digit recognition

### 2017-02-07 doc/Paper.tex
Add Implementation section & TODOs

\vspace{5cm}
\begin{abstract}
We implement a neural network to classify handwritten digits. The training is done in parallel, using MPI. We provide a comparison for model hyper-parameters and for training time vs number of processes. It achieves great accuracy and fast training time. An interactive demo is also presented
\end{abstract}

\newpage
\tableofcontents

\newpage
\section{Problem statement}
\label{sec:problem}
Given a picture of a handwritten digit, label it accordingly 0 - 9.

@@

\newpage
\section{Model}
\label{sec:model}
We use a back-propagation neural network:
\begin{align*}
W^{(k)} &= W^{(k-1)} + \alpha \nabla_W^{(k-1)} \\ 
b^{(k)} &= b^{(k-1)} + \alpha \nabla_b^{(k-1)}
\end{align*}
Where $W$ is the weights matrix, $10 \times 784$ -- the number of classes( one for each digit) and the dimension of an image ($28 \times 28$). $b$ is the bias vector, $1 \times 10$, corresponding to the free element. $W^{(k)}$ denotes the weights at step $k$. $\nabla$ represents the update which must produce to improve prediction.
\\

@@

@@

\newpage
\bibliographystyle{ieeetr}
	\bibliography{references} % expects file "references.bib"
	\addcontentsline{toc}{section}{References}

>>>>

\vspace{5cm}
\begin{abstract}
TODO: rewrite when paper is done, talk about each section

We implement a neural network to classify handwritten digits. The training is done in parallel, using MPI. We provide a comparison for model hyper-parameters and for training time vs number of processes. It achieves great accuracy and fast training time. An interactive demo is also presented
\end{abstract}

% \newpage
% \pagestyle{plain}
% \tableofcontents

\newpage
TODO: introduction?

\section{Problem statement}
\label{sec:problem}
Given a picture of a handwritten digit, label it accordingly 0 - 9.

@@

\newpage
\section{Model}
\label{sec:model}
In order to recognize a given image, we need to model to understand the data. It needs to be able to be queried for a new instance in order to provide an interactive demo.
\\

We use a back-propagation neural network:
\begin{align*}
W^{(k)} &= W^{(k-1)} + \alpha \nabla_W^{(k-1)} \\ 
b^{(k)} &= b^{(k-1)} + \alpha \nabla_b^{(k-1)}
\end{align*}
Where $W$ is the weights matrix, $10 \times 784$ -- the number of classes( one for each digit) and the dimension of an image ($28 \times 28$). $b$ is the bias vector, $1 \times 10$, corresponding to the free element. $W^{(k)}$ denotes the weights at step $k$. $\nabla$ represents the update which must produce to improve prediction.
\\

@@

\paragraph{Prediction}
TODO

@@

\newpage
\section{Parallelization}
Parallelism is needed in the training phase of the model, as prediction happens instantaneously

TODO: talk about matrix multiplication overhead

TODO: graph of train time vs nr of processors

\newpage
\section{Graphical Interface}
TODO: picture of resizing

TODO: picture of GUI

\newpage
\section{Implementation}
After going through the high-level overview of the project, we now delve into implementation details.

\paragraph{Predictive model} The core of the project is implemented in C++. This includes the neural network training and prediction. Data is maintained in memory using vectors from the standard library.

\paragraph{Graphical Interface} The GUI is implemented as a web page in HTML, with a canvas for the input box.
The drawing is facilitated by the Sketch library \cite{sketch}. Interactivity and picture resizing is done through JavaScript.

\paragraph{Communication Server} The glue between the front-end and the model is a web-server done in Python, using the Flask library \cite{flask}. An array of $784$ pixels is received through from the GUI and is passed to the compiled executable. The output (predicted digit and prediction confidence) is then passed back through AJAX.
\\

The entire source code is available at \url{https://github.com/stefan1niculae/mnist-in-mpi}.

\vspace{\fill} % place references at the bottom
\bibliographystyle{ieeetr}
	\bibliography{references} % expects file "references.bib"
	\addcontentsline{toc}{section}{References}
